\begin{definition} \label{definition:weak_infty_category}
    \TODO{this definition is not very precise}
An \hldef{$\infty$-category} (or \hldef{weak $\infty$-category}) is a category-like structure that encodes morphisms of all dimensions, where composition is associative and unital only up to coherent higher homotopies.  
More precisely, one usually works with the notion of an \hldef{$(\infty,1)$-category}, in which all $k$-morphisms for $k>1$ are invertible up to higher homotopy.  

Formally, an $\infty$-category can be defined in several equivalent ways, each specifying a precise model of this higher structure.  
Each of the standard models forms an \textit{$\infty$-cosmos} — a simplicially enriched category whose hom-objects are themselves $\infty$-categories — and all such models are equivalent up to categorical equivalence.  
Common frameworks include:

\begin{itemize}
  \item \textbf{Quasicategories:} Simplicial sets $C$ satisfying the \hldef{inner horn-filling condition}:  
  for every $n \ge 2$ and $0 < i < n$, every map $\Lambda_i[n] \to C$ (where $\Lambda_i[n]$ is the $i$th inner horn of the standard simplex $\Delta[n]$) extends to a map $\Delta[n] \to C$.  
  Such objects are the fibrant objects in the Joyal model structure on simplicial sets.

  \item \textbf{Complete Segal spaces:} Simplicial spaces $W_\bullet: \Delta^{\mathrm{op}} \to \mathbf{sSet}$ satisfying the Segal condition  
  $$
  W_n \simeq W_1 \times_{W_0} \cdots \times_{W_0} W_1
  $$
  (encoding associative composition up to homotopy) together with the completeness condition ensuring that equivalences are detected correctly.  
  These are the fibrant objects in the Rezk model structure on simplicial spaces.

  \item \textbf{Simplicial categories:} Categories enriched in simplicial sets whose hom-objects are Kan complexes and satisfy homotopy-coherent associativity laws.  
  These are related to quasicategories via the homotopy coherent nerve construction.

  \item \textbf{Other equivalent models:} Segal categories, naturally marked simplicial sets, and $\Theta$-spaces, each giving a distinct but equivalent encoding of higher categorical coherence.
\end{itemize}

Morphisms between $\infty$-categories, called \hldef{$\infty$-functors}, are maps in the chosen model that preserve the higher compositional structure up to coherent homotopy.  
The totality of $\infty$-categories and $\infty$-functors forms an $(\infty,2)$-category commonly denoted by \hl{$\infty\text{-}\mathbf{Cat}$}.

In summary, an $\infty$-category formalizes the idea of a category enriched in homotopy types (or spaces) — a “category up to higher coherent homotopies.”  
All standard models of $\infty$-categories (quasicategories, complete Segal spaces, simplicial categories, etc.) are equivalent in the sense of $\infty$-cosmoi theory.
\end{definition}