\begin{definition} \label{definition:examples_of_common_categories}
We introduce the following common examples of categories, together with some frequently used notational variants:

\begin{itemize}
    \item The \hldef{category of sets}\CrefIfExists{definition:category_of_sets}, denoted \hl{$\mathbf{Set}$}, also written \hl{$\mathrm{Set}$}, \hl{$\mathbf{Sets}$}, or \hl{$(\mathbf{Set})$}, has objects all sets and morphisms all set-theoretic functions.
    \item The \hldef{category of groups}\CrefIfExists{definition:group_homomorphism}, denoted \hl{$\mathbf{Grp}$}, also written \hl{$\mathrm{Grp}$} or \hl{$\mathbf{Groups}$}, has objects all \CrefAndHyperrefIfExist{definition:group}{groups} and morphisms all \CrefAndHyperrefIfExist{definition:group_homomorphism}{group homomorphisms}.
    \item The \hldef{category of abelian groups}, denoted \hl{$\mathbf{Ab}$}, also written \hl{$\mathrm{Ab}$} or \hl{$\mathbf{AbGrp}$}, has objects all \CrefAndHyperrefIfExist{definition:group_homomorphism}{abelian groups} and morphisms all \CrefAndHyperrefIfExist{definition:group_homomorphism}{group homomorphisms}.
    \item Given a \CrefAndHyperrefIfExist{definition:ring}{not-necessarily commutative ring with unity $R$}, the \hldef{category of (left/right/two-sided)$R$-modules}, denoted \hl{$\mathbf{Mod}_R$}, also written \hl{$R\text{-Mod}$}, has objects all (left/right/two-sided)$R$-modules and morphisms the \CrefAndHyperrefIfExist{definition:homomorphism_of_modules_over_a_ring}{$R$-module homomorphisms}.
    \item Given a field $k$, the \hldef{category of vector spaces over $k$}, denoted \hl{$\mathbf{Vect}_k$}, also written \hl{$k\text{-Vect}$} or \hl{$\mathrm{Vect}(k)$}, has objects all $k$-vector spaces and morphisms all $k$-linear maps.
    \item The \hldef{category of topological spaces}, denoted \hl{$\mathbf{Top}$}, also written \hl{$\mathrm{Top}$} or \hl{$\mathbf{TopSpaces}$}, has objects all topological spaces and morphisms all continuous maps.
    \item The \hldef{category of rings}, denoted \hl{$\mathbf{Ring}$}, also written \hl{$\mathrm{Ring}$}, has objects all rings with unity and morphisms all unital ring homomorphisms.
    \item The \hldef{category of commutative rings}, denoted \hl{$\mathbf{CRing}$}, also written \hl{$\mathrm{CRing}$} or \hl{$\mathbf{CommRing}$}, has objects all commutative rings with unity and morphisms all unital ring homomorphisms.
    \item The \hldef{category of fields}, denoted \hl{$\mathbf{Field}$}, also written \hl{$\mathrm{Field}$} or \hl{$\mathbf{Fields}$}, has objects all fields and morphisms all field homomorphisms.
    \item The \hldef{category of monoids}, denoted \hl{$\mathbf{Mon}$}, also written \hl{$\mathrm{Mon}$} or \hl{$\mathbf{Monoids}$}, has objects all monoids and morphisms all monoid homomorphisms.
    \item The \hldef{category of semigroups}, denoted \hl{$\mathbf{SemiGrp}$}, also written \hl{$\mathrm{SGrp}$} or \hl{$\mathbf{Semigroups}$}, has objects all semigroups and morphisms all semigroup homomorphisms.
    \item Given a topological space $X$, the \hldef{category of sheaves of sets on $X$}, denoted \hl{$\mathbf{Sh}(X)$}, also written \hl{$\mathrm{Sh}(X)$}, has objects all sheaves of sets on $X$ and morphisms all morphisms of sheaves.
    \item The \hldef{category of small categories}, denoted \hl{$\mathbf{Cat}$}, also written \hl{$\mathrm{Cat}$} or \hl{$\mathbf{Categories}$}, has objects all \CrefAndHyperrefIfExist{definition:locally_small_category}{small categories} and morphisms all \CrefAndHyperrefIfExist{definition:functor_between_categories}{functors} between them.
    % \item Given a category $\mathcal{C}$, its \hldef{opposite category}, denoted \hl{$\mathcal{C}^{\mathrm{op}}$}, also written \hl{$\mathcal{C}^{op}$}, has objects the same as $\mathcal{C}$ but with morphisms reversed.
    \item Given categories $\mathcal{C}$ and $\mathcal{D}$, the \hldef{functor category}\CrefIfExists{definition:diagram_in_a_category_indexed_by_a_small_category}, denoted \hl{$[\mathcal{C},\mathcal{D}]$}, also written \hl{$\mathrm{Fun}(\mathcal{C},\mathcal{D})$}, has objects all functors from $\mathcal{C}$ to $\mathcal{D}$ and morphisms all natural transformations between them.
\end{itemize}
\end{definition}