\begin{lemma}[cf. {\cite[Flat Resolution Lemma 3.2.8]{weibel}}] \label{lemma:flat_resolution_lemma_of_tor_objects_of_abelian_categories_with_a_right_exact_bifunctor_assuming_that_category_has_enough_projectives_or_flats}
Let $\mathcal{A}, \calB, \calC$ be \CrefAndHyperrefIfExist{definition:abelian_category}{abelian categories}, and let $\otimes : \mathcal{A} \times \mathcal{B} \to \mathcal{C}$ be a \CrefAndHyperrefIfExist{definition:n_ary_additive_functor_between_additive_categories}{biadditive functor}
that is \CrefAndHyperrefIfExist{definition:exact_functor_between_abelian_categories}{right exact} in each variable. 
Let $A \in \calA$ and $B \in \calB$ be objects.
\begin{enumerate}
    % \item Suppose that $A \in \calA$ is an object with a \CrefAndHyperrefIfExist{definition:left_right_resolution_of_a_class_of_objects_in_an_abelian_category}{projective resolution}. For any object $B \in \calB$, the objects
    % $$\mathrm{Tor}_n^{\mathcal{A}}(A, B) \in \calC$$
    % obtained via a \CrefAndHyperrefIfExist{definition:left_right_resolution_of_a_class_of_objects_in_an_abelian_category}{projective resolution of $A$} and via a \CrefAndHyperrefIfExist{definition:flat_resolution_of_an_object_in_an_abelian_category_with_respect_to_a_right_exact_monoidal_product_functor}{flat resolution of $A$} are naturally isomorphic. 

    \item Suppose that $\mathcal{A}$ \CrefAndHyperrefIfExist{definition:has_enough_injectives_or_projectives_for_an_abelian_category}{has enough projective objects}.
    % or \CrefAndHyperrefIfExist{definition:has_enough_flat_objects_for_an_abelian_category_with_respect_to_a_right_exact_bifunctor}{has enough flat objects}.
    Suppose that $A$ has some \CrefAndHyperrefIfExist{definition:flat_resolution_of_an_object_in_an_abelian_category_with_respect_to_a_right_exact_monoidal_product_functor}{flat resolution}. The \CrefAndHyperrefIfExist{definition:tor_functors_of_a_right_exact_monoidal_functor_on_an_abelian_category}{Tor objects} 
    $$\mathrm{Tor}_n(A, B) \in \calC$$
    obtained via a \CrefAndHyperrefIfExist{definition:left_right_resolution_of_a_class_of_objects_in_an_abelian_category}{projective resolution of $A$} and via a \CrefAndHyperrefIfExist{definition:flat_resolution_of_an_object_in_an_abelian_category_with_respect_to_a_right_exact_monoidal_product_functor}{flat resolution of $A$} are naturally isomorphic. In particular, either notion of $\Tor_n$ is well defined.


    % \item Suppose that $B \in \calB$ is an object with a \CrefAndHyperrefIfExist{definition:left_right_resolution_of_a_class_of_objects_in_an_abelian_category}{projective resolution}. For any object $A \in \calA$, the objects
    % $$\mathrm{Tor}_n^{\mathcal{A}}(A, B) \in \calC$$
    % obtained via a \CrefAndHyperrefIfExist{definition:left_right_resolution_of_a_class_of_objects_in_an_abelian_category}{projective resolution of $B$} and via a \CrefAndHyperrefIfExist{definition:flat_resolution_of_an_object_in_an_abelian_category_with_respect_to_a_right_exact_monoidal_product_functor}{flat resolution of $B$} are naturally isomorphic. 

    \item Suppose that $\mathcal{B}$ \CrefAndHyperrefIfExist{definition:has_enough_injectives_or_projectives_for_an_abelian_category}{has enough projective objects}.
    % or \CrefAndHyperrefIfExist{definition:has_enough_flat_objects_for_an_abelian_category_with_respect_to_a_right_exact_bifunctor}{has enough flat objects}.
    Suppose that $B$ has some \CrefAndHyperrefIfExist{definition:flat_resolution_of_an_object_in_an_abelian_category_with_respect_to_a_right_exact_monoidal_product_functor}{flat resolution}. The Tor objects 
    $$\mathrm{Tor}_n(A, B) \in \calC$$
    obtained via a \CrefAndHyperrefIfExist{definition:left_right_resolution_of_a_class_of_objects_in_an_abelian_category}{projective resolution of $B$} and via a \CrefAndHyperrefIfExist{definition:flat_resolution_of_an_object_in_an_abelian_category_with_respect_to_a_right_exact_monoidal_product_functor}{flat resolution of $B$} are naturally isomorphic. In particular, either notion of $\Tor_n$ is well defined.


\end{enumerate}
\end{lemma}

\begin{proof}

    We show $1$. Write $\Tor_n(A,B)$ for the tor object obtained via a projective resolution of $A$. Write $H_n(F_\bullet \otimes B)$ for the tor object obtained via a flat resolution $F_\bullet \to A$ of $A$. We argue by induction. For $n = 0$, we have $\Tor_0(A,B) \cong H_0(F_\bullet \otimes B)$ because $- \otimes B$ is right exact by assumption. 
   
    Let $K$ be such that $0 \to K \to F_0 \to A$ is exact. write $E_\bullet = (\cdots \to F_2 \to F_1)$ so that $E_\bullet \to K$ is a resolution of $K$ by flat objects (\Cref{lemma:an_object_of_abelian_category_with_enough_objects_of_a_class_on_the_right_left_has_right_left_resolution_by_the_class}). Since $\calA$ has enough projectives, further note that all flat objects are \CrefAndHyperrefIfExist{definition:F_acyclic_object_for_a_left_or_right_functor_between_abelian_categories}{acyclic} for the functor $- \otimes B$ by \Cref{lemma:flat_objects_are_acyclic_for_tensoring_by_any_object_if_enough_projectives_or_flats_exist}.
    
    By \Cref{lemma:dimension_shifting_lemma_for_acyclic_syzygies}, we have 
    $$\Tor_1(A,B) = \ker(K \otimes B \to F_0 \otimes B) = \ker \left\{ \frac{F_1 \otimes B}{\operatorname{im}(F_2 \otimes B) \to F_0 \otimes B} = H_1(F \otimes B)  \right\},$$
    thus establishing the desired isomorphism for $n = 1$. For $n \geq 2$, use induction to see that 
    $$\Tor_n(A,B) \cong \Tor_{n-1}(K, B) \cong H_{n-1}(E_\bullet \otimes B) = H_n(F \otimes B).$$

\end{proof}