\begin{proposition} \label{proposition:examples_of_abelian_categories}
The following are examples of \CrefAndHyperrefIfExist{definition:abelian_category}{abelian categories}:

\begin{enumerate}
    \item The category of $R$-$S$ bimodules where $R$,$S$ are \CrefAndHyperrefIfExist{definition:ring}{(not necessarily commutative) rings} (\Cref{theorem:the_category_of_R_S_bimodules_is_a_grothendieck_abelian_category_and_AB4_star}).

    \item The category $\mathbf{Ab}$ of abelian groups and group homomorphisms is abelian.

    \item The category $\text{Vect}_k$ of vector spaces over a field $k$ and $k$-linear maps is abelian.

    \item More generally, if $R$ is a \CrefAndHyperrefIfExist{definition:noetherian_ring}{noetherian ring}, then the category of \CrefAndHyperrefIfExist{definition:finitely_generated_modules_over_rings}{finitely generated} $R$-modules is abelian.

    \item For a \CrefAndHyperrefIfExist{definition:ringed_space}{ringed space} $(X, \mathcal{O}_X)$, the category of \CrefAndHyperrefIfExist{definition:module_over_a_sheaf_of_rings_on_a_site}{$\mathcal{O}_X$-modules} is abelian.
    \TODO{a quasi-coherent sheaf on a locally ringed space}
    \item If $X$ is a \CrefAndHyperrefIfExist{definition:scheme}{scheme} (or more generally a \CrefAndHyperrefIfExist{definition:locally_ringed_space_on_a_topological_space}{locally ringed space}), the category of \CrefAndHyperrefIfExist{definition:quasi_coherent_sheaf_on_a_general_scheme}{quasi-coherent sheaves on $X$} is abelian.
    \item For any \CrefAndHyperrefIfExist{definition:essentially_small_category}{essentially small category} $\mathcal{C}$ and any abelian category $\mathcal{A}$, the \CrefAndHyperrefIfExist{definition:diagram_in_a_category_indexed_by_a_small_category}{functor category $[\mathcal{C}, \mathcal{A}]$} and the category $\PreShv(\calC, \calA)$ of \CrefAndHyperrefIfExist{definition:presheaf_on_a_category}{presheaves} are abelian.
    \TODO{apparently, the essentially smallness condition is removable, provided that the sheafification functor exists. However, the essentially small assumption is needed to show that the category of sheaves of $O$-modules is a Grothendieck abelian caetgory. Verify all this. Moreover, when working with a big site of a scheme, one typically fixes a unvierse or work relative to a cardinal cutoff to treat it as essentially small}

    \item For any \CrefAndHyperrefIfExist{definition:grothendieck_topology_on_a_category_site_covering_sieve_topologically_generating_family}{site} $(\calC, J)$ on an \CrefAndHyperrefIfExist{definition:essentially_small_category}{essentially small category} $\mathcal{C}$ and any abelian category $\mathcal{A}$, the category $\Shv(\calC, \calA)$ of \CrefAndHyperrefIfExist{definition:sheaf_on_a_site}{sheaves} is abelian.

    \item For any \CrefAndHyperrefIfExist{definition:grothendieck_topology_on_a_category_site_covering_sieve_topologically_generating_family}{site} $(\calC, J)$ on an \CrefAndHyperrefIfExist{definition:essentially_small_category}{essentially small category} $\mathcal{C}$ and a \CrefAndHyperrefIfExist{definition:sheaf_on_a_site}{sheaf of rings} $\calO$ on $\calC$, the category $\mathbf{Mod}(\mathcal{O})$ of \CrefAndHyperrefIfExist{definition:module_over_a_sheaf_of_rings_on_a_site}{$\calO$-modules} is an abelian category.

\end{enumerate}
\end{proposition}