\begin{theorem}[Balancing generalized derived functors of a biadditive functor of abelian categories computed via flat resolutions] \label{theorem:balancing_generalized_derived_functors_of_a_biadditive_functor_of_abelian_categories_computed_via_flat_resolutions}
    Let $F: \calA \times \calB \to \calC$ be a \CrefAndHyperrefIfExist{definition:n_ary_additive_functor_between_additive_categories}{biadditive functor} of \CrefAndHyperrefIfExist{definition:abelian_category}{abelian categories}. Assume that (small) filtered colimits which exist in $\calC$ are exact (e.g. which holds if $\calC$ satisfies \CrefAndHyperrefIfExist{definition:grothendiecks_additional_axioms_for_abelian_categories}{Ab5}).

    Let $A \in \calA$ and $B \in \calB$ be objects. 
    \begin{enumerate}
        \item Suppose that \CrefAndHyperrefIfExist{definition:left_right_resolution_of_a_class_of_objects_in_an_abelian_category}{left resolutions} $P_{A,\bullet} \to A$ and $P_{B,\bullet} \to B$ exist such that $F(P_{A,i}, -): \calB \to \calC$ and $F(-, P_{B,i}): \calA \to \calC$ are exact for all $i$, i.e. $P_{A,\bullet}$ and $P_{B,\bullet}$ are \CrefAndHyperrefIfExist{definition:flat_resolution_of_an_object_in_an_abelian_category_with_respect_to_a_right_exact_monoidal_product_functor}{flat resolutions} of $A$ and $B$ respectively. 
        \begin{enumerate}
            \item The objects \CrefAndHyperrefIfExist{definition:generalized_derived_functors_for_biadditive_functors_of_abelian_categories_via_resolutions_by_flat_objects}{$L_n^{I}F(A,B)$} and $L_n^{II}F(A,B)$ are naturally isomorphic.
            \item The objects $L_n^{I}F(A,B)$ and $L_n^{II}F(A,B)$ are well defined (up to natural isomorphism), i.e. do not depend on the choice of left resolutions of $A$ and $B$ respectively.
        \end{enumerate}

        \item Suppose that \CrefAndHyperrefIfExist{definition:left_right_resolution_of_a_class_of_objects_in_an_abelian_category}{right resolutions} $A \to I^{A,\bullet}$ and $B \to I^{B,\bullet}$ exist such that $F(I^{A,i}, -): \calB \to \calC$ and $F(-, I^{B,i}): \calA \to \calC$ are exact for all $i$. 
        \begin{enumerate}
            \item The objects \CrefAndHyperrefIfExist{definition:generalized_derived_functors_for_biadditive_functors_of_abelian_categories_via_resolutions_by_flat_objects}{$R^n_{I}F(A,B)$} and $R^n_{II}F(A,B)$ are naturally isomorphic.
            \item The objects $R^n_{I}F(A,B)$ and $R^n_{II}F(A,B)$ are well defined (up to natural isomorphism), i.e. do not depend on the choice of left resolutions of $A$ and $B$ respectively.
        \end{enumerate}
    \end{enumerate}
\end{theorem}

\begin{proof}

    We prove 1. The other part is the dual statement.

    Choose resolutions $P_{A,\bullet} \xrightarrow{\varepsilon} A$ and $P_{B,\bullet} \xrightarrow{\eta} B$ such that $F(P_{A,i}, -): \calB \to \calC$ and $F(-, P_{B,i}): \calA \to \calC$ are exact for all $i$. As per \Cref{lemma:applying_biadd_func_to_res_is_defined_up_to_quasi_iso_and_agrees_with_the_tot_complex_of_the_double_complex_of_the_biadd_func_on_the_two_res}, $F(\varepsilon, \id)$ is a quasi-isomorphism and hence $H_*(\Tot(F(P_{A,\bullet}, P_{B,\bullet}))) \xrightarrow{H_*(F(\varepsilon, P_{B,\bullet}))} H_*(F(A, P_{B,\bullet}))$ is a natural isomorphism.  By symmetry, there is a natural isomorphism $H_*(\Tot(F(P_{A,\bullet} P_{B,\bullet}))) \xrightarrow{} H_*(F(P_{A,\bullet}, B))$. Therefore, $L_n^I(A,B)$ and $L_n^{II}(A,B)$ are naturally isomorphic as claimed. In particular, $L_n^{I}(A,B)$ and $L_n^{II}(A,B)$ are independent of the choice of resolution of $A$ and $B$ respectively.

\end{proof}